%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%   PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\usepackage{setspace}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}
\usepackage{enumitem}
\usepackage{microtype}

% \allowdisplaybreaks
% \usepackage[usenames,dvipsnames]{xcolor}
% \usepackage{emerald}% for signature font

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue
}

\begin{document}

%----------------------------------------------------------------------------------------
%   TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.72\textwidth}
    \vspace{-\baselineskip} % Required for vertically aligning minipages

    { 
        \begin{minipage}{0.6\textwidth}
        \fontsize{16}{20} {\textbf{\MakeUppercase{Subhrajyoty Roy}}}            
        \end{minipage}
        \hfill
        \begin{minipage}{0.4\textwidth}
            \small
            \icon{MapMarker}{11}{\textbf{Nationality:} Indian}\vspace{-1.5mm}\\
            \icon{Phone}{11}{(+91) 80139 76355}\vspace{-1.5mm}\\
            \icon{Envelope}{11}{\href{mailto:roysubhra98@gmail.com}{roysubhra98@gmail.com}}\vspace{-1.5mm}\\
        \end{minipage}
    
    } % First name
\end{minipage}
\hfill
\begin{minipage}{0.27\textwidth}
    \vspace{0.75\baselineskip}  % Required for vertically aligning minipages
    {
        \small
        \icon{GraduationCap}{11}{\href{https://scholar.google.com/citations?user=Gocm0lYAAAAJ&hl=en&authuser=1}{Google Scholar}}\vspace{-2mm}\\
        \icon{Github}{11}{\href{https://github.com/subroy13}{github.com/subroy13}}\vspace{-1.5mm}\\
        \icon{LinkedinSquare}{11}{\href{https://www.linkedin.com/in/subroy13}{/in/subroy13}}\vspace{-1.5mm}\\
        \icon{Globe}{11}{\href{https://www.statwizard.in}{Portfolio Website}} 
    }
\end{minipage}

% -------------------------
% Introduction
% -------------------------
\cvsect{Current Positions}
\vspace{-14pt}

\begin{itemize}[noitemsep, leftmargin=*]
    \item \emph{Ph.D. Candidate} in Statistics from \textbf{Indian Statistical Institute, Kolkata} specializing in robust statistics and minimum divergence estimation with a focus on developing scalable matrix factorization algorithms for high-dimensional data.
    \item \emph{Principal Information Researcher} at \textbf{SysCloud Inc.} with a focus on developing tools for business automation using machine learning and generative AI solutions.
\end{itemize}

% ----------------
% Interests
% ---------------
\cvsect{Research Interests}
\vspace{-15pt}

% \begin{itemize}[noitemsep, leftmargin=*]
%     \item Robust and High-dimensional statistical inference.
%     \item Unsupervised Machine Learning.
%     \item Spatio-temporal and functional data analysis.
%     \item Adversarial Impact and Fairness in Machine Learning and Neural Networks.
% \end{itemize}

\begin{itemize}[noitemsep, leftmargin=*]
    \item Robust and High-dimensional statistical inference.
    \item Statistical divergences and minimum distance estimation.
    \item Spatio-temporal data analysis.
    \item Robust Machine Learning and Adversarial Neural Networks.
    \item Statistical applications in finance and environmental Sciences.
\end{itemize}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCES
%----------------------------------------------------------------------------------------
\vspace{-12pt}
\cvsect{Professional Experience}
\begin{entrylist}
    \entry
    {July, 2022\\ - June, 2025}
    {Principal Information Researcher}
    {SysCloud Inc.}
    {\vspace{-7pt}\small
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Continuous system improvement, research and new technology development across the company.
            \item Implementing a centralized control flow system to reduce resource overconsumption, resulting in $90\%$ reduction in API rate-limit errors.
            \item Development of SysCloud Sky and Scout, the AI-powered chatbots for customer and internal usage.  
            \item Building company-wide automation and adoption to customized AI solutions using prompting, RAG, AI agents, etc.
        \end{itemize}
    }
    \entry
    {May, 2024\\-July, 2024}
    {Mentor}
    {Great Learning Education Series Pvt. Ltd.}
    {\vspace{-7pt}\small
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt,leftmargin=10pt]
            \item Course instructor for \textit{Mathematics for Artificial Intelligence} module. Received a consistent rating of 4.5+.
        \end{itemize}
    }
    \entry
    {July, 2021\\- June, 2022}
    {Data Scientist}
    {SysCloud Inc.}
    {\vspace{-7pt}\small
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Developed models for optimized bidding strategy for Google Ads using reinforcement learning.
            \item Unified, scalable and robust system architecture development of backup, restore and export of any cloud, resulting in business expansion for various SaaS apps (Quickbooks, Hubspot, Salesforce, Slack, Box, etc.).
        \end{itemize}
    }
    \entry
    {2020\\\footnotesize{May - June}}
    {Data Scientist Intern}
    {General Electric (Aviation)}
    {\vspace{-7pt}\small
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Understanding of the impact of COVID-19 on the aviation industry with an analysis of historical tweets data.
        \end{itemize}
    }
    \entry
    {2019\\\footnotesize{May - June}}
    {Data Scientist Intern}
    {SysCloud Inc.}
    {\vspace{-7pt}
    \small
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=10pt]
            \item Developed cost optimization techniques for backup and restore of G-suite and Office 365 workspaces.
            \item Solving phishing email detection problem using a combination of NLP and Deep learning.
        \end{itemize}
    }
\end{entrylist}


%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
% \vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
    {2021 - Current}
    {Ph.D. in Statistics (External Research Fellow)}
    {Indian Statistical Institute, Kolkata}
    {\textbf{Thesis:} Robust Matrix Factorization using the Density Power Divergence and its Applications. \\
    \textbf{Supervisors:} Prof. Ayanendranath Basu and Prof. Abhik Ghosh.}
    \entry
    {2019-2021}
    {Masters of Statistics (M.Stat.)}
    {Indian Statistical Institute, Kolkata}
    {Grade: $93.8\%$, Financial Statistics specialization, Ranked \emph{1st}.}
    \entry
    {2016 - 2019}
    {Bachelor of Statistics (B.Stat.)}
    {Indian Statistical Institute, Kolkata}
    {Grade: $93.6\%$, Ranked \emph{2nd}.}
    \entry
    {2014 - 2016}
    {Higher Secondary (WBCHSE)}
    {Nimta High School, Kolkata}
    {Grade: $93.4\%$, District Rank \emph{2nd}.}
    \entry
    {2014}
    {Secondary (WBCSSE)}
    {Nimta High School, Kolkata}
    {Grade: $94.57\%$, State Rank \emph{20th}.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%   Publications
%----------------------------------------------------------------------------------------
\vspace{-15 pt}
\cvsect{Publications}

\textbf{Journal Articles}
\begin{enumerate}
    \item \textbf{Roy, S.}, Sarkar, A., Ghosh, A., \& Basu, A. (2023). Asymptotic Breakdown Point Analysis for a General Class of Minimum Divergence Estimators. \emph{arXiv preprint} arXiv:2304.07466. (\textit{To be appeared in ``Bernoulli''}). \href{https://arxiv.org/abs/2304.07466}{[Link]}.
    \item \textbf{Roy, S.}, Basu, A., \& Ghosh, A. (2024). Robust Principal Component Analysis using Density Power Divergence. \emph{Journal of Machine Learning Research}, 25(324), 1-40. \href{https://www.jmlr.org/papers/v25/23-1096.html}{[Link]}.
    \item \textbf{Roy, S.}, Ghosh, A., \& Basu, A. (2024). Robust singular value decomposition with application to video surveillance background modelling. \emph{Statistics and Computing}, 34(5), 178. \href{https://link.springer.com/article/10.1007/s11222-024-10493-7}{[Link]}.
    \item Pyne, A., \textbf{Roy, S.}, Ghosh, A., \& Basu, A. (2024). Robust and efficient estimation in ordinal response models using the density power divergence. \emph{Statistics}, 58(3), 481-520. \href{https://www.tandfonline.com/doi/abs/10.1080/02331888.2024.2347329}{[Link]}.        
    \item Bhaduri, R., \textbf{Roy, S.}, \& Pal, S. K. (2022). Rough-Fuzzy CPD: a gradual change point detection algorithm. \emph{Journal of Data, Information and Management}, 4(3), 243-266. \href{https://link.springer.com/article/10.1007/s42488-022-00077-3}{[Link]}.
    \item Ghatak, A., Singh Patel, S., Bonnerjee, S., \& \textbf{Roy, S.} (2022). A generalized epidemiological model with dynamic and asymptomatic population. \emph{Statistical Methods in Medical Research}, 31(11), 2137-2163. \href{https://journals.sagepub.com/doi/abs/10.1177/09622802221115877}{[Link]}.
    \item \textbf{Roy, S.}, Sengupta, D., Rudra, K., \& Saha, U. S. (2020). Analysis of Pollution Patterns in Regions of Kolkata. \emph{Calcutta Statistical Association Bulletin}, 72(2), 133-170. \href{https://journals.sagepub.com/doi/abs/10.1177/0008068320976781}{[Link]}.
    \item Mukherjee, D., Dalal, A., \& \textbf{Roy, S.} (2019). Feasibility of Transparent Price Discovery in Tea through Auction in India. \emph{Commodity Insights Yearbook (MCX)}, 44-52. \href{https://www.mcxindia.com/docs/default-source/about-us/commodity-insights-yearbook/2019/02-emerging-trends/feasibility-of-transparent-price-discovery-in-tea-through-auction-in-india-dr-diganta-mukherjee-mr-abhinandan-dalal-and-mr-subhrajyoty-roy.pdf}{[Link]}.
\end{enumerate}

\textbf{Preprints}
\begin{enumerate}
    \item Deb, S., Neves, C., \& \textbf{Roy, S.} (2024). Nonparametric quantile regression for spatio-temporal processes. \emph{arXiv preprint} arXiv:2405.13783. \href{https://arxiv.org/abs/2405.13783}{[Link]}.
    \item \textbf{Roy, S.} (2024). Trustworthy Dimensionality Reduction. \emph{arXiv preprint} arXiv:2405.05868. (\textit{Master's dissertation thesis}). \href{https://arxiv.org/abs/2405.05868}{[Link]}.
    \item Bhaduri, R., Bonnerjee, S., \& \textbf{Roy, S.} (2019). Onset detection: A new approach to QBH system. \emph{arXiv preprint} arXiv:1908.07409. (\textit{Undergraduate group project}). \href{https://arxiv.org/abs/1908.07409}{[Link]}.
\end{enumerate}

\vspace{0.1cm}
\textbf{Working Projects}
\begin{enumerate}
    \item \textbf{Roy, S.}, Deb, S., Karmakar, S. \& Roy, R. (2024+). Nonparametric Regression of Spatio-temporal Data using Infinite Dimensional Covariates.
    \item \textbf{Roy, S.}, Basu, S., Ghosh, A. \& Basu, A. (2024+). Generalized Alpha-Beta Divergence, Associated Entropy and its Properties.
    % \item \textbf{Roy, S.}, Basu, S., Ghosh, A. \& Basu, A. (2024+). Asymptotic Breakdown Point Analysis for Minimum Generalized Alpha-Beta Divergence Estimator.
    \item Jana, S., \textbf{Roy, S.}, Basu, A. \& Ghosh, A. (2024+). Asymptotic Breakdown Point Analysis of Minimum Density Power Divergence Estimator under Independent Non-homogeneous Observations.
\end{enumerate}


% ----------------
% Talks and Conferences
% ----------------
\cvsect{Seminars, Conferences \& Lectures}
\vspace*{-10pt}

\begin{enumerate}
    \item Student Paper Competition at \textbf{IISA Conference, 2024} at \textbf{Cochin University of Science and Technology}. \\
    \emph{Title:} Robust Principal Component Analysis using Density Power Divergence.
    \item Contributory talk at \textbf{IMS Asia Pacific Rim Meeting, 2024} at \textbf{University of Melbourne}. \\
    \emph{Title:} A novel and scalable background modelling algorithm from video surveillance data.
    \item Invited guest lecture for Robust Statistics course (M.Stat.'22) at \textbf{Indian Statistical Institute, Kolkata}.\\
    \emph{Title:} A review of Robust Location and Scatter estimators.
    \item Prasanta Chandra Mahalanobis memorial lecture at \textbf{Indian Statistical Institute, Kolkata}.\\
    \emph{Title:} Algorithmic Fairness of Statistical Decision Systems.
    \item D. Basu memorial lecture at \textbf{Indian Statistical Institute, Kolkata}.\\
    \emph{Title:} tSNE: A way to visualize multivariate data.
\end{enumerate}


% ---------------------------
% Projects
% --------------------------
\cvsect{Projects}
\begin{entrylist}
    \vspace{-10pt}
    \entry
    {2023}
    {Multi PDF Querybot}
    {\href{https://github.com/subroy13/multi-pdf-querybot}{Github Link}}
    {\small It is a streamlit application to chat with PDF documents using RAG and large language models. It uses a locally hosted Chroma Vector database, SQLite database for metadata storage, and Anthropic Claude model for access to foundational LLM.}
    \vspace{-5pt}\\
    \entry
    {2020}
    {COVID-19 Tracker: A Dashboard for prediction and control assistance}
    {}
    {\small Developed a dashboard to visualize the COVID-19 situation in different states of India. It dynamically estimates the time-varying reproduction rate and prediction of COVID-19 spread for various lockdown scenarios for district levels in India, based on a modified eSIR model. The project was funded by the Indian Insititute of Management, Vishakhapatnam.}
    \entry
    {2019\\Class Project}
    {Analysis of Climber's challenges in scaling Mount Rainier}
    {\href{https://github.com/subroy13/mount-rainier-case-study}{Report Link} }
    {\small Modelling of climber's success rate in climbing Mount Rainier based on weather modelling. Modelling of climber's team sizes for insights about mountaineering-based local economy.}
    \entry
    {2019\\Class Project}
    {An Introduction of Causal Inference using Direct Acyclic Graph}
    {\href{https://www.statwizard.in/aboutme/causal-dag/final-report.pdf}{Report Link} }
    {\small Understanding of the setup and assumptions for causal inference. Estimating the effect of intervention using frontdoor and backdoor criterion, simulations and applications to real-world datasets to estimate causality.}
    \entry
    {2018}
    {Chatbot using Seq2Seq Attention Mechanism}
    {\href{https://github.com/subroy13/seq2seq-attention-bot}{Github Link}}
    {\small It is a chatbot created with a seq2seq neural network with a basic attention mechanism, trained with the Cornell Movie Corpus dataset.}
\end{entrylist}

% --------------------
% Tools
% -------------------
\cvsect{Tools and Packages}

\begin{entrylist}
    \entry
    {2024}
    {\texttt{Langchain} - Contributor}
    {\href{https://github.com/langchain-ai/langchain/commits?author=subroy13}{Github Commits}}
    {\small Largest framework for developing applications powered by large language models}
    \vspace*{-5pt}
    \entry
    {2023}
    {\texttt{Multi PDF QueryBoot} - Developer \& Maintainer}
    {\href{https://github.com/subroy13/multi-pdf-querybot}{Github Link}}
    {\small A streamlit application to chat with PDF documents using RAG and Large language models}
    \vspace*{-5pt}
    \entry
    {2023}
    {\texttt{callgrid-reader} - Developer \& Maintainer}
    {\href{https://www.npmjs.com/package/callgrind-reader}{NPM Link}}
    {\small A typescript utility package to read, parse and analyze callgrind files for profiling analysis of codes}
    \vspace*{-5pt}
    \entry
    {2023}
    {\texttt{decompy} - Developer \& Maintainer}
    {\href{https://pypi.org/project/decompy/}{PyPI Link}}
    {\small Python package for multiple robust matrix and tensor decomposition algorithms}
    \vspace*{-5pt}
    \entry
    {2022}
    {\texttt{roufcp} - Developer \& Maintainer}
    {\href{https://pypi.org/project/roufcp/}{PyPI Link}}
    {\small Python package implementing a gradual changepoint detection algorithm using rough-fuzzy set theory}
    \vspace*{-5pt}
    \entry
    {2021}
    {\texttt{rsvddpd} - Developer \& Maintainer}
    {\href{https://cran.r-project.org/web/packages/rsvddpd/index.html}{CRAN Link}}
    {\small R package to perform Robust SVD using Density Power Divergence}
\end{entrylist}


%----------------------------------------------------------------------------------------
%   Accolades
%----------------------------------------------------------------------------------------
\vspace{-0.2cm}
\cvsect{Accolades}
\begin{entrylist}
    \vspace*{-0.5cm}
    \entry
    {2024}
    {Nominated for the Student Paper Award}
    {IISA Conference 2024}
    {}
    \vspace*{-0.5cm}
    \entry
    {2024}
    {AWS Cloud Practitioner Certification}
    {Amazon Web Services (AWS)}
    {}
    \vspace*{-0.5cm}
    \entry
    {2023}
    {AIR 6 at National Eligibility Test}
    {Council of Scientific and Industrial Research (CSIR), Govt. of India}
    {}
    \vspace*{-0.5cm}
    \entry
    {2022}
    {Nominated for P. C. Mahalanobis Memorial Gold Medal}
    {Indian Statistical Institute, Kolkata}
    {}
    \vspace*{-0.5cm}
    \entry
    {2022}
    {J. K. Ghosh Memorial Gold Medal}
    {Indian Statistical Institute, Kolkata}
    {}
    \vspace*{-0.5cm}
    \entry
    {2016-2021}
    {Dean's list of toppers}
    {Indian Statistical Institute, Kolkata}
    {}
    \vspace*{-0.5cm}
    \entry
    {2020}
    {Scaled score 324 at GRE General Test}
    {Educational Testing Service (ETS)}
    {}
    \vspace*{-0.5cm}
    \entry
    {2020}
    {Nikhilesh Bhattacharya Memorial Gold Medal}
    {Indian Statistical Insititute, Kolkata}
    {}
    \vspace*{-0.5cm}
    \entry
    {2020}
    {D. Basu Memorial Gold Medal}
    {Indian Statistical Insititute, Kolkata}
    {}
    \vspace*{-0.5cm}
    \entry
    {2019}
    {93 percentile at GRE Mathematics Subject Test}
    {Educational Testing Service (ETS)}
    {}
    \vspace*{-0.5cm}
    \entry
    {2018}
    {1st Quartile at Simon Marais Mathematical Competition}
    {Australian Mathematical Science Insititute}
    {}
    \vspace*{-0.5cm}
    \entry
    {2016}
    {AIR 1 in Undergraduate Entrance Exam}
    {Insititute of Mathematics and Application, Bhubaneshwar}
    {}
\end{entrylist}

% \pagebreak
% ---------------
% Skills
% ---------------

\cvsect{Skills}
\vspace{-6pt}

\begin{tabular}{p{3cm}l}
    \textbf{Programming} & R, Python, SQL, PHP, JavaScript (NestJS, NodeJS, React, NextJS).\\
    \textbf{Technologies} & AWS (S3, Lambda, ECS, Sagemaker, Bedrock), Docker, Langchain, Langflow.\\
    \textbf{Tools} & MS-Office, \LaTeX\\
\end{tabular}

% --------------
% Activities
% ---------------

% \vspace{-6 pt}
\cvsect{Activities}
\vspace{-6pt}
\begin{itemize}[noitemsep]
    \item Maintain a substack newsletter \href{https://statwizard.substack.com/?showWelcome=true}{StatWizard} with 200+ subscribers.
    \item Served as a session chair for IMS Asia-Pacifim Rim Meeting 2024 at the University of Melbourne, Australia.
\end{itemize}

%-----------------------------------------------------------------------------------
%   REFERENCES
%----------------------------------------------------------------------------------------
\vspace{-6pt}
\cvsect{References}
\vspace{-6pt}
\begin{itemize}[noitemsep]
    \item \textbf{Ayaendranath Basu.} Professor, Indian Statistical Institute, Kolkata. \href{mailto:ayanbasu@isical.ac.in}{ayanbasu@isical.ac.in}
    \item \textbf{Abhik Ghosh.}  Associate Professor, Indian Statistical Institute, Kolkata. \href{mailto:abhik.ghosh@isical.ac.in}{abhik.ghosh@isical.ac.in}
    \item \textbf{Diganta Mukherjee.} Professor, Indian Statistical Institute, Kolkata. \href{mailto:diganta@isical.ac.in}{diganta@isical.ac.in}
    \item \textbf{Soudeep Deb.} Associate Professor, Indian Institute of Management, Bangalore. \href{mailto:soudeep@iimb.ac.in}{soudeep@iimb.ac.in}
    \item \textbf{Vijay Krishna.} CEO, SysCloud Inc. \href{mailto:vijay@syscloudsoftware.com}{vijay@syscloudsoftware.com}
\end{itemize}




%----------------------------------------------------------------------------------------
%   LANGUAGES
%----------------------------------------------------------------------------------------
% \vspace{-6 pt}
% \cvsect{Languages}
% \vspace{-6pt}
% % Bengali (Native), English, Hindi.

% \begin{minipage}{0.45\textwidth}
%     \begin{itemize}[noitemsep]
%         \item \textbf{English} - Professional Working proficiency
%         \item \textbf{Hindi} - Professional Working proficiency
%     \end{itemize}
% \end{minipage}
% \hfill
% \begin{minipage}{0.45\textwidth}
%     \begin{itemize}[noitemsep]
%         \item \textbf{Japanese} - Elementary proficiency
%         \item \textbf{Bengali} - Native proficiency
%     \end{itemize}
% \end{minipage}


%----------------------------------------------------------------------------------------

% \vspace{1cm}
\textit{I certify that the information provided above is true and accurate to the best of my knowledge}
\begin{flushright}
    --- {\textit{Subhrajyoty Roy}}
\end{flushright}

\end{document}